### 2018-08-07 doc/plos/text/manuscript.tex
add relative metrics table
And some commentary.

To assess accuracy at finer geographic resolutions, we report MAE relative to
the naive and simple baselines (measured as the ratios MASE and RelMAE
respectively). When aggregating errors over multiple geographic units (e.g.
states within some region) we report the geometric mean of errors as this
yields a result that can still be interpreted as a ratio.

TODO (python3 analyze.py metrics)

@@

>>>>

To assess accuracy at finer geographic resolutions, we report MAE relative to
the naive and simple baselines (measured as the ratios MASE and RelMAE
respectively). When aggregating errors over multiple geographic units (e.g.
states within some region) we report the geometric mean of errors as this
yields a result that can still be interpreted as a ratio. The relative errors
are summarized in Table~\ref{table_relative_metrics}.

% python3 analyze.py metrics
\begin{table}[!ht]
  \centering
  \caption{{\bf Relative error across sets of locations.}}
  \begin{tabular}{|l|l|l|}
    \hline
    {\bf Locations (n)} & {\bf G.M. MASE} & {\bf G.M. RelMAE}\\ \thickhline
    US National (1) & 0.667 & 0.799 \\ \hline
    Census Divisions (9) & 0.853 & 0.859 \\ \hline
    HHS Regions (10) & 0.865 & 0.849 \\ \hline
    Atoms in HHS1 (6) & 0.960 & 0.918 \\ \hline
    Atoms in HHS2 (5) & 1.094 & 1.068 \\ \hline
    Atoms in HHS3 (6) & 1.019 & 0.900 \\ \hline
    Atoms in HHS4 (8) & 0.996 & 0.886 \\ \hline
    Atoms in HHS5 (6) & 0.955 & 0.912 \\ \hline
    Atoms in HHS6 (5) & 0.941 & 0.941 \\ \hline
    Atoms in HHS7 (4) & 0.995 & 0.928 \\ \hline
    Atoms in HHS8 (6) & 1.029 & 0.991 \\ \hline
    Atoms in HHS9 (4) & 1.048 & 0.863 \\ \hline
    Atoms in HHS10 (4) & 1.014 & 0.929 \\ \hline
    All Atoms (54) & 1.002 & 0.931 \\ \hline
  \end{tabular}
  \begin{flushleft}
    TODO(define atom, enumerate "all atoms", mention naive/simple, define GM)
  \end{flushleft}
  \label{table_relative_metrics}
\end{table}

At the national level, the sensor fusion nowcast has lower error than either
baseline by a considerable margin. The same is true for Census divisions and
HHS regions collectively, although the margin is not as large. Aggregated over
individual atoms, either within a particular region or altogether, the sensor
fusion nowcast seems to generally be on par with the naive baseline and
somewhat better than the simple baseline. For atoms within HHS region 2
specifically, the sensor fusion nowcast has higher overall error than both
naive and simple baselines.

@@

TODO(why is hhs2 the worst? PR/VI: least ground truth, extreme noise, disparate
dynamics, no sensors other than sar3; NY, JFK: inferred.)

TODO(more discussion)
